A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-10-24 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
added conclusion

\subsection{Effects of Node failures, Group Size and Stake Distributions}
To evaluate the possible effects of node failure and stake distributions on group and signature 
characteristics, we use the multi-run study. We then observe trends in the specific parameters 
discussed below. We also run each multi run study for each of the three distribitions to study 
the correlation between the observed trends and the type of stake distribution.

\textit{Group Size} in all distributions group size appears to reduce the percentage
of lynchpinned signatures and compromised groups. why?

\textit{Failure percent}

@@

\newpage
\section{Conclusion and Future work}
\begin{itemize}
\item Dynamic systems -Transfer functions instead of stochastic representations?
\item Utility functions
\item Genetic Algorithms
\item Additional questions
\end{itemize}

>>>>

\subsection{Effects of Node failures, Group Size and Stake Distributions}
To evaluate the possible effects of node failure and stake distributions on group and signature 
characteristics, we use the multi-run study. We then observe trends in the specific parameters 
discussed below. We also run each multi run study for each of the three distribitions to study 
the correlation between the observed trends and the type of stake distribution. Additionally, byzantine
taking the median measures of each variable, we hope to address the fluctuations due to distributions with
increased centralization.

\textit{Group Size} in all distributions group size appears to reduce the percentage
of lynchpinned signatures and compromised groups. Intuitively this makes since since 
as we increase the size of a group, we include more group owners who may not be malicious. 
comment on degree of change?

\textit{Node Failure percent} appears to significantly impact the lynchpinned signature percentage
but have little to no effect on compromised groups. Why?

\textit{Distribution} centralization appears to minimally affect these trends but, it is very likeley
that the use of the median for each run is the cause of this. We would expect that highly centralized
distributions would cause fluctuations in these values similar to their effect on the final steady state 
level. This is primarily due to the ownership of a larger number of nodes by a few operators in highly 
centralized distributions.

@@

\newpage
\section{Conclusion and Future work}
This theoretical analysis highlighted possible behaviors of the Keep network beacon. we
validated the model using some simple analytical methods. However, once the beacon launches
we can use real data from the network to validate and adjust the model. At this point we can
then use the model to better investigate future behaviours and causes of behavior.
